Normalized expressions

### 2021-02-26 analysis/normalized.Rmd
Parse and plot pattern

# Substitue&co

@@

# `eval(x[[condition]])` pattern

See https://cran.r-project.org/doc/manuals/r-release/R-lang.html#switch

```{r}
eval_switch <- E_cano %>% filter(has_var, has_bracket, topcall == "[[")

nb_ev_switch_call_sites <- eval_switch %>% pull(src_ref) %>% n_distinct()
```

There are `r nb_ev_switch_call_sites` call sites using that pattern.

But this is actually not correct, because we should look at the non-resolved expression to find this pattern.

>>>>

# Substitute&co

@@

# `Parse` and plotting functions

We approximate the plotting function by just looking for `plot` in their name:

```{r}
plotting <- E_cano %>% filter(str_detect(topcall, fixed("plot")))

nb_plotting_call_sites <- plotting %>% pull(src_ref) %>% n_distinct()
```

There are `r nb_plotting_call_sites` plotting call sites.

Are they built using parse? For that, we look at the non-resolved expression (`parse` will disappear after).

Currently, we use a regex. When `parsed` column is fixed, we will get more accurate results.

```{r}
parse_plot <- plotting %>% filter(str_detect(ev_expr, fixed("parse")))

nb_parse_plot_call_sites <- parse_plot %>% pull(src_ref) %>% n_distinct()
```

This already amounts to `r nb_parse_plot_call_sites` call sites.
